\documentclass[journal]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=magenta]{hyperref}

% \usepackage[all=normal, paragraphs, floats, bibnotes]{savetrees}
% \usepackage[defaultcolor=red, final]{changes}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs}
%\usepackage{gensymb}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tabularx,booktabs}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\setlength{\extrarowheight}{1pt} % for a bit more open "look"

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\ifCLASSOPTIONcompsoc
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
\usepackage[caption=false,font=footnotesize]{subfig}
\fi

% some shortcuts commands
\newcommand{\RE}[1]{\operatorname{Re}\left({#1}\right)}
\newcommand{\IM}[1]{\operatorname{Im}\left({#1}\right)}
\newcommand{\EV}[1]{\mathbb{E}\left({#1}\right)}
\newcommand{\argmin}[1]{\underset{#1}{\operatorname{argmin}}\;}
\newcommand{\argmax}[1]{\underset{#1}{\operatorname{argmax}}\;}
\newcommand{\mat}[1]{\boldsymbol{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vc}[1]{\mathrm{vec}\left({#1}\right)}
\newcommand{\cov}[1]{\mathrm{cov}\left({#1}\right)}
\newcommand{\stot}[1]{\mathrm{s2t}\left({#1}\right)}
\newcommand{\ttos}[1]{\mathrm{t2s}\left({#1}\right)}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}

\begin{document}
\bstctlcite{Settings}
\title{Symmetric--Reciprocal--Match Method for\\ Vector Network Analyzer Calibration}

\author{%
	\IEEEauthorblockN{%
	Ziad~Hatab, Michael~Ernst~Gadringer, and~Wolfgang~Bösch%\\
	%Graz University of Technology, Austria\\
	%\{z.hatab; michael.gadringer; wbosch\}@tugraz.at
	}%
	\thanks{This work was supported by the Christian Doppler Research Association and by the Austrian Federal Ministry for Digital and Economic Affairs and the National Foundation for Research, Technology, and Development}
	\thanks{Ziad~Hatab, Michael~Ernst~Gadringer and Wolfgang~Bösch are with the Institute of Microwave and Photonic Engineering, Graz University of Technology, 8010 Graz, Austria, and also with the Christian Doppler Laboratory for Technology Guided Electronic Component Design and Characterization (TONI), 8010 Graz, Austria (e-mail: \{z.hatab, michael.gadringer, wbosch\}@tugraz.at).}
	\thanks{Software implementation and measurements are available online:\\
	\url{https://github.com/ZiadHatab/srm-calibration}}
}%
\markboth{This work has been accepted for publication in the IEEE Transactions on Instrumentation and Measurement}{}
\maketitle

\begin{abstract}
This paper proposes a new approach, the symmetric-reciprocal-match (SRM) method, for calibrating vector network analyzers (VNAs). The method involves using multiple symmetric one-port loads, a two-port reciprocal device, and a matched load. The load standards consist of two-port symmetric one-port devices, and at least three unique loads are used. However, the specific impedances of the loads are not specified. The reciprocal device can be any transmissive device, although a non-reciprocal device can also be used if only the one-port error boxes are of interest. The matched load is fully defined and can be asymmetric. We demonstrated the accuracy of the proposed method with measurements of coaxial standards using a commercial METAS traceable short-open-load-reciprocal (SOLR) calibration kit with verification standards. In addition, we presented a numerical Monte Carlo analysis considering various uncertainty factors. An advantage of the proposed method is that only the match standard is defined, whereas the remaining standards are partially defined, either through symmetry or reciprocity.
\end{abstract}

\begin{IEEEkeywords}
vector network analyzer, calibration, microwave measurement
\end{IEEEkeywords}

\input{Sections/Section1}
\input{Sections/Section2}
\input{Sections/Section3}
\input{Sections/Section4}
\input{Sections/Section5}
\input{Sections/Section6}

%\appendices
%\input{Sections/AppendixA}

\section*{Acknowledgment}
The authors thank the ebsCENTER, Graz, Austria for providing access to their X-ray equipment.

\bibliographystyle{IEEEtran}
\bibliography{References/references.bib}

\input{Authors_Bio/Ziad_Hatab.tex}
\input{Authors_Bio/Michael_Gadringer.tex}
\input{Authors_Bio/Wolfgang_Boesch.tex}\vfill


\end{document}