%!TEX root = ../main.tex

\section{Conclusion}
% Summary
In this paper, we propose \tool, the first coverage-guided fuzzer for Solana programs.
\tool implements five oracles to detect common vulnerabilities in Solana programs, namely missing signer checks, missing owner checks, missing key checks, arbitrary CPIs, and integer bugs.
Moreover, \tool also implements a generic oracle based on lamport gains.
To evaluate the capability of \tool to detect these vulnerabilities, we evaluated \tool against known vulnerabilities~\cite{Neodyme2021-vw}, including the infamous Wormhole bug~\cite{Goodin2022-wormhole}, and compared its performance with VRust~\cite{Cui2022-nm}.
The evaluation has shown that \tool is able to detect the above-mentioned Solana program vulnerabilities and outperforms the state-of-the-art Solana bug detection tool.
%
We also performed an extensive evaluation in which we fuzzed \noc programs from the Solana mainnet blockchain.
We showed that \tool is the only existing approach to effectively and precisely detect bugs in Solana smart contracts, without relying on source code.
\tool reports 92 bugs in 52 programs, 14 of which we have verified as exploitable bugs at the time of writing the paper.
%
Moreover, we evaluated \tool's performance against a set of bug bounty programs consisting of complex and productively used Solana programs.
The evaluation has shown that \tool is capable to fuzz complex programs with up to \num{5211} transactions per second.
%
Our large-scale evaluation is the most extensive security analysis of the Solana blockchain known to date.
